---
title: "Logo"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    fig_width: 7
    fig_height: 7
theme: simplex
---

Source: https://github.com/markziemann/RN4CB


# Intro

In this script, I'm attempting to do some logo design with R because I don't want
to use AI for this task.

```{r,libs}

#install.packages("system_fonts")
library(systemfonts)
library(scales)
library(viridis)

```

## Make a blank chart with some text

List the available typefaces.

```{r,data}

x <- c(0,0,10,10)
y <- c(0,10,0,10)
plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
text(5,5,"RN4CB",cex=10)

myfonts <- system_fonts()
head(myfonts)
tail(myfonts)

unique(myfonts$family)

```

The number of families is less than the number of fonts due to typefaces having different width and italic styles.

## Font styles

Now we can look at the different font styles like italics and bold.

```{r,fonts}

par(mfrow=c(2,2))
plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
text(5,5,"RN4CB",family=myfonts[1,"family"],font=1, cex=2)

plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
text(5,5,"RN4CB",family=myfonts[1,"family"],font=2, cex=2)

plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
text(5,5,"RN4CB",family=myfonts[1,"family"],font=3, cex=2)

plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
text(5,5,"RN4CB",family=myfonts[1,"family"],font=4, cex=2)

par(mfrow=c(1,1))

```

Now we can show all the typefaces with all the font styles.

```{r,demonstrate_fonts}

families <- unique(myfonts$family)
families <- families[order(families)]

par(mar=c(0,1,1.5,0))

par(mfrow=c(6,4))
null <- lapply(1:length(families),function(i) {
  plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
  text(5,5,"RN4CB", family=families[i], font=1, cex=3)
  mtext(families[i],cex=1)

  plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
  text(5,5,"RN4CB", family=families[i],font=2, cex=3)

  plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
  text(5,5,"RN4CB", family=families[i],font=3, cex=3)

  plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white")
  text(5,5,"RN4CB", family=families[i],font=4, cex=3)

})

par(mfrow=c(1,1))

```


# Candidate network logo

"TeX Gyre Adventor"

```{r,network1,fig.height=4,fig.width=7}

skycols <- colors()[grep("sky",colors())]

set.seed(42) ; myseeds <- sample(0:10000)

SIZE=40
set.seed(myseeds[1]) ; x <- sample(0:10000,size=SIZE,replace=FALSE)/1000
set.seed(myseeds[2]) ; y <- sample(0:10000,size=SIZE,replace=FALSE)/1000
set.seed(myseeds[5]) ; mycols <- sample(skycols,size=length(x),replace=TRUE)

plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white",xlim=c(0,10),ylim=c(0,10))

df <- data.frame(x,y)
set.seed(myseeds[6]) ; df2 <- df[sample(1:SIZE,size=SIZE,replace=T),]
lines(df2,col="gray",lwd=1.5)
lines(df,col="lightgray",lwd=1.5)
points(x,y, cex=1.6, pch=19, col=mycols)

text(5.1,5,"RN4CB", family="TeX Gyre Adventor",font=1, cex=10)

```

# Candidate grid

```{r,network2,fig.height=4,fig.width=7}

skycols <- colors()[grep("sky",colors())]

set.seed(42) ; myseeds <- sample(0:10000)

set.seed(myseeds[1]) ; x <- sample(0:10,size=SIZE*100,replace=TRUE)
set.seed(myseeds[2]) ; y <- sample(0:10,size=SIZE*100,replace=TRUE)
set.seed(myseeds[5]) ; mycols <- sample(skycols,size=length(x),replace=TRUE)

df <- data.frame(x,y)
df <- unique(df)[1:SIZE,]

plot(df,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white",xlim=c(0,10),ylim=c(0,10))

set.seed(myseeds[6]) ; df2 <- df[sample(1:SIZE,size=SIZE,replace=T),]
lines(df2,col="gray",lwd=1.5)
lines(df,col="lightgray",lwd=1.5)
points(df, cex=1.6, pch=19, col=mycols)

text(5.1,5,"RN4CB", family="TeX Gyre Adventor",font=1, cex=10)

```

# Network chaos

This one looks OK.

```{r,network3,fig.height=6,fig.width=7}

skycols <- colors()[grep("sky",colors())]

null <- lapply(1:10,function(i) {

set.seed(i) ; myseeds <- sample(0:10000)
SIZE=25
set.seed(myseeds[1]) ; x <- sample(0:10000,size=SIZE,replace=FALSE)/1000
set.seed(myseeds[2]) ; y <- sample(0:10000,size=SIZE,replace=FALSE)/1000
set.seed(myseeds[5]) ; mycols <- sample(skycols,size=length(x),replace=TRUE)

plot(x,y,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white",xlim=c(0,10),ylim=c(0,10))

df <- data.frame(x,y)
set.seed(myseeds[6]) ; df2 <- df[sample(1:SIZE,size=SIZE,replace=T),]
lines(df2,col="darkgray",lwd=5)
lines(df,col="lightgray",lwd=5)

set.seed(myseeds[7]) ; mycex <- rnorm(n=50,mean=3.5,sd=1)

points(x,y, cex=mycex, pch=19, col=mycols)

rect(0, 3, 10, 7,col="white",border="black",lwd=3)

text(5,5,"RN4CB", family="TeX Gyre Adventor",font=1, cex=9)
mtext(i)
})

```

# Network grid

More ordered xy coords.

```{r,network4,fig.height=6,fig.width=7}

null <- lapply(c(1:10,39),function(i) {

set.seed(i) ; myseeds <- sample(0:10000)
SIZE=25
set.seed(myseeds[1]) ; x <- sample(0:10,size=SIZE*100,replace=TRUE)
set.seed(myseeds[2]) ; y <- sample(0:10,size=SIZE*100,replace=TRUE)
set.seed(myseeds[5]) ; mycols <- sample(skycols,size=length(x),replace=TRUE)

df <- data.frame(x,y)
df <- unique(df)[1:SIZE,]

plot(df,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white",xlim=c(0,10),ylim=c(0,10))

set.seed(myseeds[6]) ; df2 <- df[sample(1:SIZE,size=SIZE,replace=T),]
lines(df2,col="darkgray",lwd=5)
lines(df,col="lightgray",lwd=5)

set.seed(myseeds[7]) ; mycex <- rnorm(n=50,mean=3.5,sd=1)

points(df, cex=mycex, pch=19, col=mycols)

rect(0, 3, 10, 7,col="white",border="black",lwd=3)

text(5,5,"RN4CB", family="TeX Gyre Adventor",font=1, cex=9)
mtext(i)
})

```

# Array grid red/blue

```{r,points,fig.height=7,fig.width=7}

null <- lapply(1:10,function(i) {

set.seed(i) ; myseeds <- sample(0:10000)
SIZE=15

my_palette <- colorRampPalette(c("blue", "gray", "red"))(n = 50)

xy <- expand.grid(1:6,1:6)
set.seed(myseeds[7]) ; mycex <- rnorm(n=nrow(xy),mean=5,sd=1)
set.seed(myseeds[5]) ; mycols <- sample(my_palette,size=nrow(xy),replace=TRUE)

plot(xy,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white",xlim=c(0,7),ylim=c(0,7))

set.seed(myseeds[6]) ; df <- xy[sample(1:nrow(xy),size=SIZE,replace=T),]
set.seed(myseeds[8]) ; df2 <- xy[sample(1:nrow(xy),size=SIZE,replace=T),]

lines(df,col="lightgray",lwd=4)
lines(df2,col="darkgray",lwd=4)

points(xy, cex=mycex, pch=19, col=mycols)

rect(0.6, 2.6, 6.45, 4.4, col="white",border="black",lwd=3.5)

text(3.5,3.5,"RN4CB", family="TeX Gyre Adventor",font=1, cex=8)
mtext(i)

})

```

# Array grid Viridis

```{r,points2,fig.height=7,fig.width=7}

null <- lapply(1:10,function(i) {

set.seed(i) ; myseeds <- sample(0:10000)
SIZE=15

my_palette <-  viridis(50)

xy <- expand.grid(1:6,1:6)
set.seed(myseeds[7]) ; mycex <- rnorm(n=nrow(xy),mean=5,sd=1)
set.seed(myseeds[5]) ; mycols <- sample(my_palette,size=nrow(xy),replace=TRUE)

plot(xy,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="white",xlim=c(0,7),ylim=c(0,7))

set.seed(myseeds[6]) ; df <- xy[sample(1:nrow(xy),size=SIZE,replace=T),]
set.seed(myseeds[8]) ; df2 <- xy[sample(1:nrow(xy),size=SIZE,replace=T),]

lines(df,col="lightgray",lwd=4)
lines(df2,col="darkgray",lwd=4)

points(xy, cex=mycex, pch=19, col=mycols)

rect(0.6, 2.6, 6.45, 4.4, col="white",border="black",lwd=3.5)

text(3.5,3.5,"RN4CB", family="TeX Gyre Adventor",font=1, cex=8)
mtext(i)

})

```

# Array grid Viridis space

Now try for diamond pattern.

```{r,points3,fig.height=7,fig.width=7}

null <- lapply(1:10,function(i) {

set.seed(i) ; myseeds <- sample(0:10000)
SIZE=15

my_palette <-  viridis(50)

xy <- expand.grid(1:7,1:7)
xy <- xy[seq(2,nrow(xy),2),]
set.seed(myseeds[7]) ; mycex <- rnorm(n=nrow(xy),mean=7,sd=1)
set.seed(myseeds[5]) ; mycols <- sample(my_palette,size=nrow(xy),replace=TRUE)

plot(xy,xaxt="n", yaxt="n", xlab="",ylab="",col="white",xlim=c(0.5,7.5),ylim=c(0.5,7.5))

set.seed(myseeds[6]) ; df <- xy[sample(1:nrow(xy),size=SIZE,replace=T),]
set.seed(myseeds[8]) ; df2 <- xy[sample(1:nrow(xy),size=SIZE,replace=T),]

lines(df,col="lightgray",lwd=5)
lines(df2,col="darkgray",lwd=5)

points(xy, cex=mycex, pch=19, col=mycols)

rect(1, 3, 7, 5, col="white",border="black",lwd=3.5)

text(4,4,"RN4CB", family="TeX Gyre Adventor",font=1, cex=8)
mtext(i)

})

```

# Sin waves


```{r,sincurve,fig.height=5,fig.width=5}

curve(sin, to = 4*pi)
curve(cos, to = 4*pi,add=TRUE)

```

Now a basic plot

```{r,sin,fig.height=5,fig.width=5}

x <- seq(0,2*pi,length.out=50)
y <- sin(x)
z <- cos(x)
plot(x/2/pi*10, y, type='l',ylim=c(-2,2),lwd=2,xaxt="n", yaxt="n", bty="n",xlab="",ylab="")
lines(x/2/pi*10, z, type='l',lwd=2)

x2 <- seq(0,2*pi,length.out=10)
y2 <- sin(x2)
z2 <- cos(x2)

points(x2/2/pi*10, y2, type='p',cex=4)
points(x2/2/pi*10, z2, type='p',cex=4)

null <- lapply(1:length(x2), function(i) {
  lines(c(x2[i],x2[i])/2/pi*10 ,c(y2[i],z2[i]) ,lwd=3)
})


```

# DNA helix

Need to make it longer.

```{r,sin_long}

par(mar=c(0,1,1.5,0))

mycols <- plasma(5)[1:4]
mycols2 <- rev(mycols)

x <- seq(0,5*pi,length.out=125)
y <- sin(x)
z <- cos(x)
plot(x/2/pi*10, y, type='l',ylim=c(-1,6),lwd=15,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="darkgray")
lines(x/2/pi*10, z, type='l',lwd=12,col="darkgray")

x2 <- seq(0,5*pi,length.out=25)
y2 <- sin(x2)
z2 <- cos(x2)

points(x2/2/pi*10, y2, type='p',cex=1,col=mycols,pch=19)
points(x2/2/pi*10, z2, type='p',cex=1,col=mycols2,pch=19)

null <- lapply(1:length(x2), function(i) {
  lines(c(x2[i], x2[i])/2/pi*10, c(y2[i], mean(c(z2[i],y2[i])) ) ,lwd=15, col=mycols[i%%4+1])
  lines(c(x2[i], x2[i])/2/pi*10, c(mean(c(z2[i],y2[i])), z2[i] ) ,lwd=15, col=mycols2[i%%4+1])
})

text(10,2,"RN4CB", family="TeX Gyre Adventor",font=1, cex=10)

```

# Short helix with patchwork

Shorten by 50%

```{r,helix_long}

par(mar=c(0,1,1.5,0))

#mycols <- viridis(5)[1:4]
XMAX <- ceiling(max(x)/2/pi*10)+1
XMIN <- 0

YMIN=-1
YMAX=5
plot(x/2/pi*10, y, type='l',ylim=c(-1,5),lwd=15,xaxt="n", yaxt="n",xlab="",ylab="",col="white", bty="n")

df <- expand.grid(seq(XMIN,XMAX,2),seq(-1,4,0.5))
mycols <- rev(tail(inferno(200),50))
set.seed(42) ; points(df,pch=15,cex=7,col=sample(mycols))

mycols <- plasma(5)[1:4]
mycols2 <- rev(mycols)

x <- seq(0,5*pi,length.out=125)
y <- sin(x)
z <- cos(x)
#plot(x/2/pi*10, y, type='l',ylim=c(-1,4),lwd=15,xaxt="n", yaxt="n", bty="n",xlab="",ylab="",col="darkgray")
lines(x/2/pi*10, y, type='l',lwd=20,,col=mako(3)[2])
lines(x/2/pi*10, z, type='l',lwd=20,col=mako(3)[2])

x2 <- seq(0,5*pi,length.out=25)
y2 <- sin(x2)
z2 <- cos(x2)

points(x2/2/pi*10, y2, type='p',cex=1,col=mycols,pch=19)
points(x2/2/pi*10, z2, type='p',cex=1,col=mycols2,pch=19)

null <- lapply(1:length(x2), function(i) {
  lines(c(x2[i], x2[i])/2/pi*10, c(y2[i], mean(c(z2[i],y2[i])) ) ,lwd=15, col=mycols[i%%4+1])
  lines(c(x2[i], x2[i])/2/pi*10, c(mean(c(z2[i],y2[i])), z2[i] ) ,lwd=15, col=mycols2[i%%4+1])
})


text(10,2,"RN4CB", family="TeX Gyre Adventor",font=2, cex=10, col="black")

```

# Binary data background

```{r,bigmatrix}

mysize=42
plot(0:mysize, 0:mysize, type='p',xlim=c(0,mysize),ylim=c(0,mysize),lwd=15,xaxt="n", yaxt="n",xlab="",ylab="",col="white", bty="n")
df <- expand.grid(0:mysize,0:mysize)
#my_palette <- c("white","lightgray","gray","darkgray","black")
my_palette <- plasma(10)[6:9]
mycols <- sample(my_palette,nrow(df),replace=TRUE)
points(df,col=mycols,pch=15,cex=1.5)

rect(5, 16, 37, 26, col="white",border="black",lwd=3)

text(mysize/2,mysize/2,"RN4CB", family="TeX Gyre Adventor",font=1, cex=8, col="black")

```

rect(xleft, ybottom, xright, ytop, density = NULL, angle = 45,




## Session information

```{r,session}

sessionInfo()

```
